\chapter{Timeline window}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__window}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__window}\index{Timeline window@{Timeline window}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__window_autotoc_md4755}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__window_autotoc_md4755}%
 To access the \doxylink{namespace_timeline}{Timeline} window, select {\bfseries{Sequencing}} \texorpdfstring{$>$}{>} {\bfseries{\doxylink{namespace_timeline}{Timeline}}} from the Window menu. What the \doxylink{namespace_timeline}{Timeline} window shows depends on what you select in either the Project window or the Scene view.

For example, if you select a Game\+Object that is associated with a \doxylink{namespace_timeline}{Timeline} Asset, the \doxylink{namespace_timeline}{Timeline} window shows the tracks and clips from the \doxylink{namespace_timeline}{Timeline} Asset and the Game\+Object bindings from the \doxylink{namespace_timeline}{Timeline} instance.



{\itshape Selecting a Game\+Object associated with a \doxylink{namespace_timeline}{Timeline} Asset displays its tracks and clips, and the bindings from the \doxylink{namespace_timeline}{Timeline} instance}

If you haven’t selected a Game\+Object, the \doxylink{namespace_timeline}{Timeline} window informs you that the first step for creating a \doxylink{namespace_timeline}{Timeline} Asset and a \doxylink{namespace_timeline}{Timeline} instance is to select a Game\+Object.



{\itshape With no Game\+Object selected, the \doxylink{namespace_timeline}{Timeline} window provides instructions}

If a Game\+Object is selected and it is not associated with a \doxylink{namespace_timeline}{Timeline} Asset, the \doxylink{namespace_timeline}{Timeline} window provides the option for creating a new \doxylink{namespace_timeline}{Timeline} Asset, adding the necessary components to the selected Game\+Object, and creating a \doxylink{namespace_timeline}{Timeline} instance.



{\itshape Select a Game\+Object that is not associated with a \doxylink{namespace_timeline}{Timeline} Asset to create a new \doxylink{namespace_timeline}{Timeline} Asset, add components, and create a \doxylink{namespace_timeline}{Timeline} instance}

To use the \doxylink{namespace_timeline}{Timeline} window to view a previously created \doxylink{namespace_timeline}{Timeline} Asset, select the \doxylink{namespace_timeline}{Timeline} Asset in the Project window and open the \doxylink{namespace_timeline}{Timeline} window. The \doxylink{namespace_timeline}{Timeline} window shows the tracks and clips associated with the \doxylink{namespace_timeline}{Timeline} Asset, but without the track bindings to Game\+Objects in the Scene. In addition, the \doxylink{namespace_timeline}{Timeline} Playback Controls are disabled and there is no \doxylink{namespace_timeline}{Timeline} Playhead.



{\itshape \doxylink{namespace_timeline}{Timeline} Asset selected in the Project window shows its tracks and clips, but with no track bindings. The \doxylink{namespace_timeline}{Timeline} Playback Controls are disabled.}

\doxylink{namespace_timeline}{Timeline} saves the track bindings to Game\+Objects in the Scene with the \doxylink{namespace_timeline}{Timeline} instance, not the \doxylink{namespace_timeline}{Timeline} Asset. For details on the relationship between the Project, Scene, \doxylink{namespace_timeline}{Timeline} Assets, and \doxylink{namespace_timeline}{Timeline} instances, see \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__about}{Timeline overview}{0}. 