\chapter{Activation track properties}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__trk__act}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__trk__act}\index{Activation track properties@{Activation track properties}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__trk__act_autotoc_md4683}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__trk__act_autotoc_md4683}%
 Use the Inspector window to change the name of an Activation track and set the state of its bound Game\+Object when the \doxylink{namespace_timeline}{Timeline} Asset finishes playing.



{\itshape Inspector window when selecting an Activation track in the \doxylink{namespace_timeline}{Timeline} window}

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{3}{|X[-1]}|}
\hline
\multicolumn{2}{|l|}{\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Property}}   }}&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-3}
\endfirsthead
\hline
\endfoot
\hline
\multicolumn{2}{|l|}{\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Property}}   }}&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-3}
\endhead
\multicolumn{2}{|l|}{{\bfseries{Display Name}}   }&The name of the Activation track shown in the \doxylink{namespace_timeline}{Timeline} window and Playable Director component. The Display Name applies to the \doxylink{namespace_timeline}{Timeline} Asset and all of its \doxylink{namespace_timeline}{Timeline} instances.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Post-\/playback state}}   }&Sets the activation state for the bound Game\+Object when the \doxylink{namespace_timeline}{Timeline} Asset stops playing. The Post-\/playback state applies to the \doxylink{namespace_timeline}{Timeline} Asset and all of its \doxylink{namespace_timeline}{Timeline} instances.    \\\cline{1-3}
&Active   &Activates the bound Game\+Object when the \doxylink{namespace_timeline}{Timeline} Asset finishes playing.    \\\cline{1-3}
&Inactive   &Deactivates the bound Game\+Object when the \doxylink{namespace_timeline}{Timeline} Asset finishes playing.    \\\cline{1-3}
&Revert   &Reverts the bound Game\+Object to its activation state before the \doxylink{namespace_timeline}{Timeline} Asset began playing.~\newline
~\newline
For example, if the \doxylink{namespace_timeline}{Timeline} Asset finishes playing with the Game\+Object set to inactive, and the Game\+Object was active before the \doxylink{namespace_timeline}{Timeline} Asset began playing, then the Game\+Object reverts to active.    \\\cline{1-3}
&Leave As Is   &Sets the activation state of the bound Game\+Object to the state the \doxylink{namespace_timeline}{Timeline} Asset is at when it finishes playing.~\newline
~\newline
For example, if the \doxylink{namespace_timeline}{Timeline} Asset finishes playing with the Game\+Object set to inactive, the Game\+Object remains inactive.   \\\cline{1-3}
\end{longtabu}
