\chapter{Setting Timeline Asset properties}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__tl}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__tl}\index{Setting Timeline Asset properties@{Setting Timeline Asset properties}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__tl_autotoc_md4681}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2insp__tl_autotoc_md4681}%
 Use the Inspector window to set the frame rate, the duration mode, and a fixed length for the selected \doxylink{namespace_timeline}{Timeline} Asset. From the Project window, select a \doxylink{namespace_timeline}{Timeline} Asset to view its properties.



{\itshape Inspector window when selecting a \doxylink{namespace_timeline}{Timeline} Asset in the Project window}

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{3}{|X[-1]}|}
\hline
\multicolumn{2}{|l|}{\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Property}}   }}&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-3}
\endfirsthead
\hline
\endfoot
\hline
\multicolumn{2}{|l|}{\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Property}}   }}&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-3}
\endhead
\multicolumn{2}{|l|}{{\bfseries{Frame Rate}}   }&Sets the reference frame rate for the \doxylink{namespace_timeline}{Timeline} Asset and its \doxylink{namespace_timeline}{Timeline} instances. Change the Frame Rate to align clips at precise frames but changing the Frame Rate is only visual and has no effect on play speed, keys, tracks, or clips.~\newline
~\newline
\doxylink{namespace_timeline}{Timeline} supports the following standard frame rates\+: 24 (PAL), 25 (NTSC), 30, 50, and 60. \doxylink{namespace_timeline}{Timeline} also supports custom frame rates from 1e-\/6 to 1000.~\newline
~\newline
To set a custom frame rate, enter a non-\/standard frame rate for the Frame Rate property. In the \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__settings}{Timeline Settings}{0} menu, the Custom menu item is enabled and automatically selected for the \doxylink{namespace_timeline}{Timeline} instance. The Custom menu item shows the custom frame rate in parentheses.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Duration Mode}}   }&Choose whether the duration of the \doxylink{namespace_timeline}{Timeline} Asset extends to the end of the last clip or ends at a specific time or frame.    \\\cline{1-3}
&Based On Clips   &Sets the length of the \doxylink{namespace_timeline}{Timeline} Asset based on the end of the last clip.    \\\cline{1-3}
&Fixed Length   &Sets the length of the \doxylink{namespace_timeline}{Timeline} Asset to a specific number of seconds or frames.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Duration}}   }&Shows the length of the \doxylink{namespace_timeline}{Timeline} Asset in seconds and frames when the Duration Mode is set to Based on Clips.~\newline
~\newline
Sets the length of the \doxylink{namespace_timeline}{Timeline} Asset to a specific number of seconds or frames when the Duration Mode is set to Fixed Length.   \\\cline{1-3}
\end{longtabu}
