\chapter{Using Track groups}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2grp__use}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2grp__use}\index{Using Track groups@{Using Track groups}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2grp__use_autotoc_md4644}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2grp__use_autotoc_md4644}%
 Use Track groups to organize tracks when you are working with many tracks. For example, a \doxylink{namespace_timeline}{Timeline} Asset contains an Animation track and an Audio track that interacts with the same Game\+Object. To organize these tracks, move them into their own Track group.

To add a Track group, click the {\bfseries{Add}} button and select {\bfseries{Track Group}} from the {\bfseries{Add}} menu. You can also right-\/click an empty area of the Track list and select {\bfseries{Track Group}} from the context menu. A new Track group appears at the bottom of the Track list.



{\itshape \doxylink{namespace_timeline}{Timeline} window with Track group added}

To rename a Track group, click its name and an I-\/beam cursor appears. Type the new name for the Track group and press Return.

To move tracks into a Track group, select one or more tracks and drag over the Track group. The Track group is highlighted. When dragging a selection of tracks, the last selected track type displays beside the cursor. To drop the tracks before a specific track in the Track group, drag until a white insert line indicates the destination.



{\itshape Release the mouse button when the white insert line appears within the Track group}



{\itshape Selected tracks are moved to the location of the insert line}

A Track group can also have any number of Track sub-\/groups. To add a Track sub-\/group, either select a Track group and click the {\bfseries{Add}} button in the Track list, or click the Plus icon beside the Track group name, and select {\bfseries{Track Sub-\/\+Group}}. You can also use this menu to add tracks directly to a Track group or a Track sub-\/group.



{\itshape Click the Plus icon to add Track Sub-\/\+Groups and tracks to Track groups} 