\chapter{Nesting nodes}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-nodes}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-nodes}\index{Nesting nodes@{Nesting nodes}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-nodes_autotoc_md5413}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-nodes_autotoc_md5413}%
 Use the following nodes to work with nesting Subgraphs and State Units in a Script Graph.

For more information on Subgraphs and State Units, see \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0b052f136142546305a9d053d2653f106}{Subgraphs and State Units}{0}.

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{2}{|X[-1]}|}
\hline
\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Node}}   }&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-2}
\endfirsthead
\hline
\endfoot
\hline
\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Node}}   }&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-2}
\endhead
\doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-input-node}{{\bfseries{Input node}}}{0}   &Use an Input node to control the flow of logic and data from a Script Graph\textquotesingle{}s Subgraph node. An Input node takes data from a parent graph and makes it available to a Subgraph.    \\\cline{1-2}
\doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-output-node}{{\bfseries{Output node}}}{0}   &Use an Output node to control the flow of logic and data from a Script Graph\textquotesingle{}s Subgraph node. An Output node sends data from a Subgraph and makes it available to a parent graph.    \\\cline{1-2}
\doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-state-unit-node}{{\bfseries{State Unit node}}}{0}   &Use a State Unit node like a Subgraph. The node references and triggers a State Graph as a State Unit inside a Script Graph.    \\\cline{1-2}
\doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8visualscripting_0d1_88_80_2_documentation_0i_2vs-nesting-subgraph-node}{{\bfseries{Subgraph node}}}{0}   &Use a Subgraph node to reference and trigger another Script Graph\textquotesingle{}s logic from inside a parent Script Graph.   \\\cline{1-2}
\end{longtabu}
