\chapter{Top-\/down games}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8cinemachine_0d2_89_87_2_documentation_0i_2_cinemachine_top_down}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8cinemachine_0d2_89_87_2_documentation_0i_2_cinemachine_top_down}\index{Top-\/down games@{Top-\/down games}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8cinemachine_0d2_89_87_2_documentation_0i_2_cinemachine_top_down_autotoc_md726}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8cinemachine_0d2_89_87_2_documentation_0i_2_cinemachine_top_down_autotoc_md726}%
 \doxylink{namespace_cinemachine}{Cinemachine} Virtual Cameras are modelled after human camera operators and how they operate real-\/life cameras. As such, they have a sensitivity to the up/down axis, and always try to avoid introducing roll into the camera framing. Because of this sensitivity, the Virtual Camera avoids looking straight up or down for extended periods. They may do it in passing, but if the {\bfseries{Look At}} target is straight up or down for extended periods, they will not always give the desired result.

{\bfseries{Tip\+:}} You can deliberately roll by animating properties like {\bfseries{Dutch}} in a Virtual Camera.

If you are building a top-\/down game where the cameras look straight down, the best practice is to redefine the up direction, for the purposes of the camera. You do this by setting the {\bfseries{World Up Override}} in the \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8cinemachine_0d2_89_87_2_documentation_0i_2_cinemachine_brain_properties}{Cinemachine Brain}{0} to a Game\+Object whose local up points in the direction that you want the Virtual Camera’s up to normally be. This is applied to all Virtual Cameras controlled by that \doxylink{namespace_cinemachine}{Cinemachine} Brain. 