\chapter{Using an Animation Override track and an Avatar Mask}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2wf__mask}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2wf__mask}\index{Using an Animation Override track and an Avatar Mask@{Using an Animation Override track and an Avatar Mask}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2wf__mask_autotoc_md4772}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2wf__mask_autotoc_md4772}%
 This task demonstrates how to use an Animation Override track and an Avatar Mask to replace the upper-\/body animation of an Animation track. Use this technique to animate a humanoid to, for example, run and carry an object. For information on creating an Avatar mask, see \href{https://docs.unity3d.com/Manual/class-AvatarMask.html}{\texttt{ Avatar Mask window}}.

This task assumes that you have already \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2wf__instance}{created a Timeline instance}{0} with a simple Animation clip on an Animation track bound to a humanoid\+:



{\itshape This example uses a humanoid bound to a simple run cycle animation (Run\+Forward) that loops once}

Right-\/click the Animation track and select {\bfseries{Add Override Track}} from the context menu. An Animation Override track, named Override 0, is linked to the selected Animation track. Notice that the Animation Override track is not bound to a Game\+Object. Because the Override track is linked to the Animation track above, the Override track is bound to the same Game\+Object, in this case, the Default\+Male humanoid.



{\itshape To add an Override track, right-\/click the Animation track and select Add Override Track from the context menu\mbox{]}}

From your Project, drag an Animation Clip with upper-\/body animation into the Override track. For example, drag an animation of a humanoid standing still and waving their arms. Position and resize the clip to match the Animation clip that you want to override.



{\itshape The Animation Override track contains an Animation clip of a humanoid standing still, waving their arms (Waving\+Arms). This clip was resized to match the Animation clip (Run\+Forward) of the parent Animation track.}

Play the \doxylink{namespace_timeline}{Timeline} instance. In this example, the Waving\+Arms clip completely overrides the Run\+Forward clip. To combine the lower-\/body animation from one Animation clip with upper-\/body animation from another Animation clip, specify an Avatar Mask for the Animation Override track.



{\itshape To specify an Avatar Mask, select the Override track to view its properties in the Inspector window}

From the Project, drag an Avatar Mask, that masks the lower body animation, into the Avatar Mask property in the Inspector window. Enable the {\bfseries{Apply Avatar Mask}} checkbox. An Avatar Mask icon appears beside the track name.



{\itshape An Avatar Mask, that masks the lower body animation, is specified for the Animation Overview clip in the Inspector window. This allows the upper body animation to pass through.}



{\itshape The Avatar Mask icon (red) indicates that the Animation Override track uses an Avatar Mask.}

Play the \doxylink{namespace_timeline}{Timeline} instance. In this example, the Default\+Male humanoid uses upper-\/body animation from the Waving\+Arms clip and lower-\/body animation from the Run\+Forward clip. To temporarily disable the Avatar Mask, click the Avatar Mask icon.



{\itshape The Avatar Mask icon (red) is gray when disabled. The Waving\+Arms clip completely overrides the Run\+Forward clip.} 