\chapter{Playable Director component}
\hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2play__director}{}\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2play__director}\index{Playable Director component@{Playable Director component}}
\label{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2play__director_autotoc_md4685}%
\Hypertarget{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2play__director_autotoc_md4685}%
 The Playable Director component stores the link between a \doxylink{namespace_timeline}{Timeline} instance and a \doxylink{namespace_timeline}{Timeline} Asset. The Playable Director component controls when the \doxylink{namespace_timeline}{Timeline} instance plays, how the \doxylink{namespace_timeline}{Timeline} instance updates its clock, and what happens when the \doxylink{namespace_timeline}{Timeline} instance finishes playing.



{\itshape Playable Director component added to the Game\+Object named Ground. The Game\+Object is associated with the Ground\+CTL \doxylink{namespace_timeline}{Timeline} Asset.}

The Playable Director component also shows the list of tracks from the associated \doxylink{namespace_timeline}{Timeline} Asset ({\bfseries{Playable}} property) that animate Game\+Objects in the Scene. The link between \doxylink{namespace_timeline}{Timeline} Asset tracks and Game\+Objects in the Scene is referred to as {\bfseries{binding}} or {\bfseries{Track binding}}. For more on binding and the relationship between \doxylink{namespace_timeline}{Timeline} Assets and \doxylink{namespace_timeline}{Timeline} instances, see \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2tl__about}{Timeline overview}{0}.

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{3}{|X[-1]}|}
\hline
\multicolumn{2}{|l|}{\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Property}}   }}&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-3}
\endfirsthead
\hline
\endfoot
\hline
\multicolumn{2}{|l|}{\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Property}}   }}&\cellcolor{\tableheadbgcolor}\textbf{ {\bfseries{Description}}    }\\\cline{1-3}
\endhead
\multicolumn{2}{|l|}{{\bfseries{Playable}}   }&Associates a \doxylink{namespace_timeline}{Timeline} Asset with a Game\+Object in the Scene.~\newline
When you make this association, you create a \doxylink{namespace_timeline}{Timeline} instance for the selected \doxylink{namespace_timeline}{Timeline} Asset. After you create a \doxylink{namespace_timeline}{Timeline} instance, you can use the other properties in the Playable Director component to control the instance and choose which Game\+Objects in the Scene are animated by the \doxylink{namespace_timeline}{Timeline} Asset.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Update Method}}   }&Sets the clock source that the \doxylink{namespace_timeline}{Timeline} instance uses to update its timing.    \\\cline{1-3}
&DSP   &Select for sample accurate audio scheduling. When selected, the \doxylink{namespace_timeline}{Timeline} instance uses the same clock source that processes audio. DSP stands for digital signal processing.    \\\cline{1-3}
&Game Time   &Select to use the same clock source as the game clock. This clock source is affected by \href{https://docs.unity3d.com/Manual/TimeFrameManagement.html}{\texttt{ time scaling}}.    \\\cline{1-3}
&Unscaled Game Time   &Select to use the same clock source as the game clock, but without being affected by time scaling.    \\\cline{1-3}
&Manual   &Select to not use a clock source and to manually set the clock time through scripting.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Play on Awake}}   }&Whether the \doxylink{namespace_timeline}{Timeline} instance is played when game play is initiated. By default, a \doxylink{namespace_timeline}{Timeline} instance is set to begin as soon as the Scene begins playback. To disable the default behaviour, disable the Play on Awake option in the Playable Director component.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Wrap Mode}}   }&The behaviour when the \doxylink{namespace_timeline}{Timeline} instance ends playback.    \\\cline{1-3}
&Hold   &Plays the \doxylink{namespace_timeline}{Timeline} instance once and holds on the last frame until playback is interrupted.    \\\cline{1-3}
&Loop   &Plays the \doxylink{namespace_timeline}{Timeline} instance repeatedly until playback is interrupted.    \\\cline{1-3}
&None   &Plays the \doxylink{namespace_timeline}{Timeline} instance once.    \\\cline{1-3}
\multicolumn{2}{|l|}{Initial Time   }&The time (in seconds) at which the \doxylink{namespace_timeline}{Timeline} instance begins playing. The Initial Time adds a delay in seconds before the \doxylink{namespace_timeline}{Timeline} instance actually begins. For example, when Play On Awake is enabled and Initial Time is set to five seconds, if you click the Play button in the \doxylink{namespace_unity}{Unity} Toolbar, \href{https://docs.unity3d.com/Manual/GameView.html}{\texttt{ Play Mode}} starts and the \doxylink{namespace_timeline}{Timeline} instance begins five seconds later.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Current Time}}   }&Views the progression of time according to the \doxylink{namespace_timeline}{Timeline} instance in the \doxylink{namespace_timeline}{Timeline} window. The Current Time field matches the Playhead Location field.~\newline
Use the Current Time field when the \doxylink{namespace_timeline}{Timeline} window is hidden. The Current Time field appears in the Playable Director Component when in \doxylink{namespace_timeline}{Timeline} Playback mode or when \doxylink{namespace_unity}{Unity} is in Game Mode.    \\\cline{1-3}
\multicolumn{2}{|l|}{{\bfseries{Bindings}}   }&Shows the link between Game\+Objects in the Scene with tracks from the associated \doxylink{namespace_timeline}{Timeline} Asset (Playable property). The Bindings area is split into two columns\+:~\newline
The first column lists the tracks from the \doxylink{namespace_timeline}{Timeline} Asset. Each track is identified by an icon and its track type.~\newline
The second column lists the Game\+Object linked (or bound) to each track.~\newline
The Bindings area does not list Track groups, Track sub-\/groups, or tracks that do not animate Game\+Objects. The \doxylink{namespace_timeline}{Timeline} window shows the same bindings in the \doxysectlink{md__hey_tea_9_2_library_2_package_cache_2com_8unity_8timeline_0d1_87_85_2_documentation_0i_2trk__list__about}{Track list}{0}.   \\\cline{1-3}
\end{longtabu}
